### 2016-02-02 config/styles.inc.tex
Clean up special histogram figure

>>>>

\pgfplotsset{degradationBox/.style={area legend,solid,draw=none,fill=TangoOrange1,opacity=0.7}}
\pgfplotsset{degradationMedian/.style={color=TangoOrange3,solid,line width=2.0pt,opacity=0.7}}
\pgfplotsset{degradationMarks/.style={color=TangoScarletRed2,only marks,mark=triangle*,mark options={solid,fill=TangoScarletRed1,rotate=180},opacity=0.7}}

\pgfplotsset{enhancementBox/.style={area legend,solid,draw=none,fill=TangoSkyBlue1!80!white,opacity=0.7}}
\pgfplotsset{enhancementMedian/.style={color=TangoSkyBlue2,solid,line width=2.0pt,opacity=0.7}}
\pgfplotsset{enhancementMarks/.style={color=TangoChameleon3,only marks,mark=triangle*,mark options={solid,fill=TangoChameleon2},opacity=0.7}}

\pgfplotsset{percentileLines/.style={black,dashed}}
